Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 examples.tex
+

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \;\ast}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\<[\vaddr:=\texttt{fpaddr}]>\theta),\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{r} \_ \; \ast}_{\rtv}$
$\specline{\ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{aligned va} \ast\sumwalkabs\vaddr\qfrac\fpaddr}_{\rtv}$

@@

in Specification Line 7 ($\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\;(\texttt{wzero 64})$), we save it to \textsf{r14} to be updated later in Line 9.

@@

The crux point in the proof is updating the virtual L1 address (\textsf{pte\_addr}) to show the fresly allocated page address (\textsf{fpaddr}) in Line 22 to obtain
\[$\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr}$\]
so that when we unfold the $\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr})$ we will be able obtain a full ownerhsip on the L1 table physical pointsto $\paddr \mapsto_{\mathsf{p}} \textsf{fpaddr}$ . Then, we can split this full-ownership into to obtain a fractional ownership (q4) on it ($\paddr \mapsto_{\mathsf{p}} \{q4\} \;\textsf{fpaddr}$). Finally, we can connect this fragmental ownership with the L4-L2 physical table pointstos (Specification Lines 4-6) to obtain the complete physical table-walk assertion (L4\_L1\_PointsTo(rtv maddr l4e l3e l2e pa)).

>>>>

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \ast }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \; \ast}_{\rtv}$
$\specline{\ulcorner \texttt{aligned fpaddr} \urcorner \ast \texttt{rax}\mapsto_{r} \texttt{fpaddr} \ast \texttt{aligned va} \ast\sumwalkabs\vaddr\qfrac\textsf{fpaddr}}_{\rtv}$

@@

in Specification Line 7 ($\texttt{pte\_addr} \mapsto_{\textsf{vpte}}  \; \paddr\;(\texttt{wzero 64})$), we save it to \textsf{r14} to be updated later in Line 9.

@@

The crux point in the proof is updating the virtual L1 address (\textsf{pte\_addr}) to show the fresly allocated page address (\textsf{fpaddr}) in Line 22 to obtain
\[\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr}  \qquad\qquad (\textsf{by Rule} \TirNameStyle{WriteToVirtMemFromReg})\]
by Rule \TirNameStyle{WriteToVirtMemFromReg} which allows proving virtual address updates without exposing its internal physical page-table memory accesses. 
Consequently, right at this point in the proof, when we unfold the $\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr})$ we will be able obtain a full ownerhsip on the L1 table physical pointsto $\paddr \mapsto_{\mathsf{p}} \textsf{fpaddr}$ . Then, we can split this full-ownership into to obtain a fractional ownership (q4) on it ($\paddr \mapsto_{\mathsf{p}} \{q4\} \;\textsf{fpaddr}$). Finally, we can connect this fragmental ownership with the L4-L2 physical table pointstos (Specification Lines 4-6) to obtain the complete physical table-walk assertion (L4\_L1\_PointsTo(rtv maddr l4e l3e l2e pa)).
